### 2016-07-06 motivation.tex
Shrunk Fig. 4.
Minor edit.

\begin{figure}
\centering
\subcaptionbox {
  \label{fig:hb-eg-1}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.6]{Figures/hb-eg-1}
}
\subcaptionbox {
  \label{fig:hb-eg-2}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.6]{Figures/hb-eg-2}
}
\subcaptionbox {
  \label{fig:hb-eg-3}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.6]{Figures/hb-eg-3}
}
\subcaptionbox {
  \label{fig:hb-eg-4}
}{
  \includegraphics[scale=0.6]{Figures/hb-eg-4}
}

@@

Fig.~\ref{fig:motiv-eg-1-hb} is a visualization of $\hbZ$ from \C{Wd2}
to \C{Wd1} allowed by $\psi_{RC}$ and $\psi_{SI}$. Arrows in all
executions are legal under $\psi_{RC}$ because in no execution does an
operation $\eta_1$ from \C{Wd1} happen-before $\eta_2$ of \C{Wd2}
without the commit of \C{Wd1} also happening before $\eta_2$.
$\psi_{SI}$ however disallows $\hbZ$ arrows (hence executions) in
Figs.~\ref{fig:hb-eg-2},~\ref{fig:hb-eg-3}, and~\ref{fig:hb-eg-4}
because such arrows establish $\hbZ$ edges between (operations in)
\C{Wd2} and only a subset of the operations in \C{Wd1}. Since the
result of an operation (\eg a read) depends on what happens before
that operation, the structure of the $\hbZ$ relation ultimately
dictates the final result of the program. The arrows in
Figs.~\ref{fig:hb-eg-1} and~\ref{fig:hb-eg-2} denote $\hbZ$
relationships that do not affect the value of \C{B} in a way that
causes the program to violate its post-condition. In contrast, arrows
in Figs.~\ref{fig:hb-eg-3} and~\ref{fig:hb-eg-4} denote $\hbZ$
relationships that lead to the violation of the post-condition. The
task of the reasoning framework is to determine if all $\hbZ$
relationships allowed by an isolation level lead to the satisfaction
of the post-condition.

>>>>

\begin{figure}
\centering
\subcaptionbox {
  \label{fig:hb-eg-1}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.5]{Figures/hb-eg-1}
}
\subcaptionbox {
  \label{fig:hb-eg-2}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.5]{Figures/hb-eg-2}
}
\subcaptionbox {
  \label{fig:hb-eg-3}
} [
  0.25\columnwidth
] {
  \includegraphics[scale=0.5]{Figures/hb-eg-3}
}
\subcaptionbox {
  \label{fig:hb-eg-4}
}{
  \includegraphics[scale=0.5]{Figures/hb-eg-4}
}

@@

Fig.~\ref{fig:motiv-eg-1-hb} is a visualization of $\hbZ$ from \C{Wd2}
to \C{Wd1} allowed by $\psi_{RC}$ and $\psi_{SI}$. Arrows in all
executions are legal under $\psi_{RC}$ because in no execution does an
operation $\eta_1$ from \C{Wd1} happen-before $\eta_2$ of \C{Wd2}
without the commit of \C{Wd1} also happening before $\eta_2$.
$\psi_{SI}$ however disallows $\hbZ$ arrows (hence executions) in
Figs.~\ref{fig:hb-eg-2},~\ref{fig:hb-eg-3}, and~\ref{fig:hb-eg-4}
because such arrows establish $\hbZ$ edges between (operations in)
\C{Wd2} and only a subset of the operations in \C{Wd1}. Since the
result of an operation (\eg a read) depends on what happens before
that operation, the structure of the $\hbZ$ relation ultimately
dictates the final result of the program. The arrows in
Figs.~\ref{fig:hb-eg-1} and~\ref{fig:hb-eg-2} denote $\hbZ$
relationships that do not affect the value of \C{B} in a way that
causes the program to violate its post-condition. In contrast, arrows
in Figs.~\ref{fig:hb-eg-3} and~\ref{fig:hb-eg-4} denote $\hbZ$
relationships that lead to the violation of the post-condition. The
task of the reasoning framework is to determine if \emph{all} $\hbZ$
relationships allowed by an isolation level lead to the satisfaction
of the post-condition.
